\section{Critical Reflection}
\label{criticalreflection}

First of all, I would like to thank my supervisors Claire Blackman and Simon Cross, as they were always available to help me when stuck. The regular weekly meetings 
were also greatly appreciated as they allowed me to set weekly goals, with a short deadline to combat procrastination.


Regarding the project, I feel like I grossly underestimated the amount of work that would be needed to produce a functional compiler 
as suggested initially in the thesis proposal, even for an extremely simple compiler. Another aspect I did not expect to be a factor was computing time,
when running the tests, as the screenshots show, single qubit gates could undergo hundreds of tests in a couple of seconds, however 
when testing two-qubit gates, compute time could last up to two hours for a single test.  This also considerably slowed down 
the pace at which results could be obtained. 
These two factors were the most significant as to why I was not able to stick to the initial plan, which, in retrospect, was already quite ambitious. However I am very happy with how far I got,
although I wasn't able to produce a functional compiler, I now have a good idea of how feasible the project is.


This was also my first time coding with limited documentation and made me greatly appreciate how important producing good quality documentation along with the code is crucial for anyone to be able to work on the project.


Overall I am very satisfied with how the project ended up playing out, the challenging nature of it forcing me to learn a great deal in the process.

